\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{fontspec}
\usepackage{parskip}

% Use Helvetica Neue
\setmainfont{Helvetica Neue}[
  BoldFont = Helvetica Neue Medium,
  ItalicFont = Helvetica Neue Italic
]

\geometry{margin=1in}
\pagenumbering{gobble}

\begin{document}

\begin{center}
{\Large\bfseries Email Draft to Peter}\\[0.3cm]
{\small Re: Waxfeed Campaign Funding}
\end{center}

\rule{\textwidth}{0.5pt}

\vspace{0.5cm}

\textbf{Subject:} Waxfeed Marketing Campaign --- Funding \& Structure

\vspace{0.5cm}

Hey Peter,

Hope you're doing well. Following up on our conversation with the WBRU consultant about the marketing campaign for Waxfeed.

I've put together a campaign plan (attached) for a Q1 2025 launch. The budget I'm proposing is \$10K:
\begin{itemize}
    \item \$2K builder stipend
    \item \$8K advertising (Instagram, Reddit, TikTok)
\end{itemize}

For structure, I think the cleanest approach is a \textbf{grant or sponsorship} --- WBRU provides the funding, gets recognition as a ``Founding Partner,'' and we keep things simple. No equity, no complex legal docs. Just a straightforward MOU.

This makes sense because:
\begin{itemize}
    \item We're actively in conversations with VCs, so keeping the cap table clean matters
    \item \$10K is really marketing spend, not investment-sized
    \item WBRU still gets the cultural alignment and PR value from the partnership
    \item We can move fast and launch in January
\end{itemize}

If WBRU is interested in taking an actual ownership stake, that's a bigger conversation that would involve different terms and a larger commitment. Happy to loop in Theo and discuss if that's something you want to explore, but it would be separate from the campaign funding.

Let me know your thoughts. I've attached the full campaign plan, a one-pager summary, and a short doc on the partnership structure.

Best,\\
Shadrack

\vspace{0.5cm}

\rule{\textwidth}{0.5pt}

\textbf{Attachments:}
\begin{enumerate}
    \item Waxfeed Campaign Plan (campaign-plan.pdf)
    \item Campaign One-Pager (one-pager.pdf)
    \item Partnership Structure (ownership-analysis.pdf)
\end{enumerate}

\end{document}
