\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{fontspec}

% Use Helvetica Neue
\setmainfont{Helvetica Neue}[
  BoldFont = Helvetica Neue Medium,
  ItalicFont = Helvetica Neue Italic
]

% Tight margins for one-pager
\geometry{margin=0.75in}

% Colors
\definecolor{waxblack}{HTML}{0A0A0A}
\definecolor{accent}{HTML}{8B5CF6}

% No page numbers
\pagenumbering{gobble}

\begin{document}

\begin{center}
{\Huge\bfseries WAXFEED}\\[0.3cm]
{\large Campaign One-Pager | \$10K Budget | Q1 2025}\\[0.2cm]
{\small Polarity Lab LLC}
\end{center}

\vspace{0.3cm}

\noindent\rule{\textwidth}{1pt}

\vspace{0.4cm}

\begin{minipage}[t]{0.48\textwidth}
\subsection*{THE OPPORTUNITY}
616M streaming subscribers. Zero social platform for music discovery. Letterboxd proved \$10M+ for film. \textbf{Music is next.}

\subsection*{THE CONCEPT}
\textbf{``Your Taste Deserves a Home''}

You're the music person. You make playlists. You text recs. But where does your taste \textit{live}?

\textbf{Waxfeed.} Reviews. Lists. Friends. Feed.

\subsection*{FOMO HOOKS}
\begin{itemize}[noitemsep,leftmargin=*]
    \item Founding Critic Badge (first 1,000)
    \item Username scarcity
    \item 100 bonus Wax for early users
\end{itemize}

\subsection*{KEY COPY}
\begin{itemize}[noitemsep,leftmargin=*]
    \item ``Music finally has its Letterboxd''
    \item ``Friends $>$ Algorithms''
    \item ``You rate films. Now rate albums.''
\end{itemize}

\subsection*{CTA}
``Claim Your Username $\rightarrow$''
\end{minipage}
\hfill
\begin{minipage}[t]{0.48\textwidth}
\subsection*{BUDGET: \$10,000}

\begin{tabular}{lr}
\textbf{Builder Stipend} & \$2,000 \\
\midrule
\textbf{Advertising} & \$8,000 \\
\quad Instagram/Meta & \$3,000 \\
\quad Reddit & \$2,000 \\
\quad TikTok Ads & \$1,500 \\
\quad TikTok Influencers & \$1,000 \\
\quad Reserve/Testing & \$500 \\
\end{tabular}

\subsection*{TARGETS}
\begin{tabular}{lr}
Signups & 2,500+ \\
CPA & $<$\$3.20 \\
Day 7 Retention & $>$30\% \\
Reviews & 1,500+ \\
\end{tabular}

\subsection*{TIMELINE}
\begin{tabular}{rl}
Wk 1 & Setup + creative \\
Wk 2 & Soft launch (organic) \\
Wk 3 & Paid launch \\
Wk 4 & Optimize \\
Wk 5--6 & Scale winners \\
\end{tabular}

\subsection*{WBRU PARTNERSHIP}
\begin{itemize}[noitemsep,leftmargin=*]
    \item Founding partner of music platform
    \item Cultural credibility + growth equity
    \item WBRU community as user base
\end{itemize}
\end{minipage}

\vspace{0.4cm}
\noindent\rule{\textwidth}{1pt}

\begin{center}
\textbf{Next Step:} Finalize ownership structure $\rightarrow$ Approve concept $\rightarrow$ Launch mid-January
\end{center}

\end{document}
