\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{fancyhdr}
\usepackage{fontspec}

% Use Helvetica Neue
\setmainfont{Helvetica Neue}[
  BoldFont = Helvetica Neue Medium,
  ItalicFont = Helvetica Neue Italic
]

\geometry{margin=1in}

\definecolor{waxgray}{HTML}{666666}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textcolor{waxgray}{\small WAXFEED PARTNERSHIP}}
\fancyhead[R]{\textcolor{waxgray}{\small POLARITY LAB LLC}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.5pt}

\titleformat{\section}
  {\Large\bfseries}{\thesection}{1em}{}[\titlerule]
\titleformat{\subsection}
  {\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

\begin{center}
{\Huge\bfseries WAXFEED}\\[0.5cm]
{\Large Partnership Structure Discussion}\\[1cm]
{\large Polarity Lab LLC}\\[0.3cm]
{\small December 2024}
\end{center}

\vspace{1cm}

\section{Overview}

Waxfeed is requesting \$10,000 from WBRU (Brown Broadcasting Services LLC) to fund a Q1 2025 marketing campaign. Before proceeding, we should align on how this funding is structured.

\vspace{0.5cm}

\textbf{Key Parties:}
\begin{itemize}[noitemsep]
    \item \textbf{Polarity Lab LLC} --- Builder/developer entity (Shadrack)
    \item \textbf{Brown Broadcasting Services LLC (WBRU)} --- Potential funder
    \item \textbf{Waxfeed} --- The product/platform
\end{itemize}

\section{Proposed Structure: Grant / Sponsorship}

The simplest path forward is for WBRU to provide the \$10K as a \textbf{grant or sponsorship} with no ownership stake.

\vspace{0.5cm}

\textbf{What WBRU Gets:}
\begin{itemize}[noitemsep]
    \item Recognition as ``Founding Partner'' on Waxfeed
    \item Logo placement and PR value
    \item Cultural alignment with WBRU's revamp as a modern music platform
    \item Access to Waxfeed's user base for WBRU programming/content
    \item First-mover advantage in college radio partnership network
\end{itemize}

\vspace{0.5cm}

\textbf{What Polarity Retains:}
\begin{itemize}[noitemsep]
    \item 100\% ownership of Waxfeed IP and entity
    \item Full decision-making authority on product direction
    \item Clean cap table for future fundraising
\end{itemize}

\vspace{0.5cm}

\textbf{Why This Makes Sense:}
\begin{itemize}[noitemsep]
    \item WBRU benefits from Waxfeed's growth without operational complexity
    \item Polarity is actively in conversations with VCs --- keeping the cap table clean is critical
    \item \$10K is a marketing spend, not an investment-sized check
    \item Both parties can focus on execution rather than legal negotiations
\end{itemize}

\section{Alternative: Equity Discussion}

If WBRU is interested in taking an ownership stake in Waxfeed, that's a separate conversation that would involve different terms and a larger commitment.

Polarity is currently in discussions with venture capital investors. Any equity arrangement with WBRU would need to be coordinated with those conversations and would likely require:

\begin{itemize}[noitemsep]
    \item A larger funding commitment from WBRU
    \item Alignment with VC term expectations
    \item Formal legal documentation (SAFE, convertible note, or priced round)
\end{itemize}

If WBRU wants to explore equity participation, me and Theo can discuss further. We're open to the conversation but want to be thoughtful about structure given ongoing fundraising.

\section{Next Steps}

\begin{enumerate}[noitemsep]
    \item \textbf{Confirm funding structure} --- Is grant/sponsorship acceptable, or does WBRU want to discuss equity?
    \item \textbf{Approve campaign plan} --- Review attached marketing plan and one-pager
    \item \textbf{Execute agreement} --- Simple MOU or sponsorship agreement
    \item \textbf{Launch campaign} --- Target mid-January 2025
\end{enumerate}

\vspace{1cm}

\begin{center}
\textit{Questions? Me and Theo can discuss.}
\end{center}

\end{document}
